Reduced plasticity and variance in physiological rates for terrestrial ectotherm populations under climate change

### 2024-01-04 ms.qmd
Fixing symbols

<p style="text-align: center;">Daniel W.A. Noble^1^, Fonti Kar^2^, Frank Seebacher^3^, Alex Bush^4^, & Shinichi Nakagawa^2^</p>

#### Affliations:
^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
^2^ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia &NewLine;  
^3^ SOLES, University of Sydney, Sydney, NSW, Australia &NewLine;  
^4^ Department of Biology, Lancaster University, Liverpool, UK

>>>>

<p style="text-align: center;">Daniel W.A. Noble^1^ $\dagger$, Fonti Kar^2^,  Alex Bush^4^, Frank Seebacher^3^ $\dagger$, & Shinichi Nakagawa^2^ $\dagger$</p>

#### Affliations:
^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia &NewLine;  
^2^ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia &NewLine;  
^3^ SOLES, University of Sydney, Sydney, NSW, Australia &NewLine;  
^4^ Department of Biology, Lancaster University, Liverpool, UK &NewLine;
^$\dagger$^ Shared senior authorship &NewLine;
^$\ddagger$^ corresponding author, daniel.noble@anu.edu.au &NewLine;
